Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Responding to a comment in Sec 6.  Taking a break for a bit and revisiting the rest tonight.

Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.\botodo{The pinball stuff felt a bit too much of a digression, I think. Jessie, could you rewrite this paragraph to say what readers should expect in the upcoming section? Perhaps mention quadrants explicitly to help readers follow the flow from the previous section. We can save the pinball text for a better opportunity.}

>>>>

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
Shifting away from discrete predictions, we turn our attention to continuous estimation settings.
More often, the continuous estimation setting does not start with a target loss, but instead with a statistic of the data that we want to estimate, such as the conditional mean, variance, or entropy.
We use Theorem~\ref{thm:cvx-flats} in conjunction with results from~\citet{frongillo2018elicitation} to prove Theorem~\ref{thm:bayes-risk-lower-bound}, which yields new bounds on the convex elicitation complexity of properties like the variance and entropy.
\botodo{The pinball stuff felt a bit too much of a digression, I think. Jessie, could you rewrite this paragraph to say what readers should expect in the upcoming section? Perhaps mention quadrants explicitly to help readers follow the flow from the previous section. We can save the pinball text for a better opportunity.\jessie{Attempting... old paragraph commented out.}}
